\LARGE Coursework \\ Module Name (CMM536)

### 2018-04-27 submission.tex
final submission

To study the dataset in more detail, let's load it into the workspace, along with the required libraries. The original dataset, as downloaded, is already split into a training and testing set. However, in order to ensure the split as indeed random and stratified, the data was re-combined into a single dataset.

@@

@@

\begin{itemize}
  \item The typing is incorrect as imported - the types should all be factors
  \item The dataset is quite sparse
  \item The columns are not named. They are defined in the readme for the dataset so we will add names later
\end{itemize}

\begin{Schunk}
\begin{Sinput}
> library(xtable)
> print(xtable(head(df)))
> str(df)
> names(df)
\end{Sinput}
\end{Schunk}
Let's also check the size of the dataset:
\begin{Schunk}
\begin{Sinput}
> #record number of rows and columns
> paste('number of columns =' , ncol(df) , '. number of rows =', nrow(df))
\end{Sinput}
\begin{Soutput}
[1] "number of columns = 117 . number of rows = 102942"
\end{Soutput}
\end{Schunk}

Now let's check the class distribution (ie do we have an approximately equal number of team 1 wins as team 2 wins?).
The distribution is indeed close to equal so we do not need to worry about class imbalance later on. It is interesting to note there is some imbalance, the reason for this is not clear but probably has something to do with the manner in which the data was collected.
\begin{Schunk}
\begin{Sinput}
> #check value distribution of response variable column
> table(df[,1])
\end{Sinput}
\end{Schunk}

@@

An advantage of this dataset is there are no missing values. This is not surprising as the data was captured using the Dota 2 API. Here we also check that each team has an equal number of heroes which is a requirement for a game:

\begin{Schunk}
\begin{Sinput}
> #check for missing values (there are none)
> sum(complete.cases(df))==nrow(df)
\end{Sinput}
\begin{Soutput}
[1] TRUE
\end{Soutput}
\begin{Sinput}
> #check there are equal number of heroes present in each team (hero values for all rows should sum to zero)
> sum((rowSums(df[5:ncol(df)]))) == 0
\end{Sinput}
\begin{Soutput}
[1] TRUE
\end{Soutput}
\end{Schunk}

As discussed above, some preprocessing is required. First, we convert all numeric columns to factors:
\begin{Schunk}
\begin{Sinput}
> df[sapply(df, is.numeric)] <- lapply(df[sapply(df, is.numeric)], as.factor)
\end{Sinput}
\end{Schunk}

The column names are added in two stages. The first four columns are named manually as specified in the dataset description.\\
The remaining columns represent the individual heros. The column names are extracted from the .json file supplied with the dataset:
\begin{Schunk}
\begin{Sinput}
> #add column names to the first few columns
> names(df)[1:4] <- c('won','cluster_id','game_mode','game_type')
> #populate the other column names
> #load in json file and use it to populate column names
> hero_names <- fromJSON(file ="dota_dataset\\heroes.json")
> for ( i in c(1:length(hero_names$heroes))){
+   names(df)[i+4] <- hero_names$heroes[[i]]$name
+ }
\end{Sinput}
\end{Schunk}

Here we drop columns that are not related to heros (this analysis is concerned only with hero choice so we drop game type and location related columns). 
One column has the same value for every entry. This was noticed during the analysis stage. The column represents a mandatory hero which muct be included in the team. Since it conveys no information it is dropped:
\begin{Schunk}
\begin{Sinput}
> #drop unwanted columns
> df <- df%>%
+   select(-c(lina, cluster_id , game_mode , game_type))
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
>#check variable balancing
>numeric_df <- sapply(df,function(x){as.numeric(as.character(x))})%>%
+  as.data.frame()%>%
+  select(-seq(1,4))

@@

>ggplot(away_team_heros,aes(x=name,y=.))+
+  geom_bar(stat="identity")+
+ theme(axis.text.x = element_text(angle = 90, hjust = 1,size=7))+
+  labs(title="number of times each hero was chosen by the away team")+
+  xlab("hero name")+
+  ylab("number of games the hero was picked")
\end{Sinput}
\end{Schunk}

@@

Inspecting the two plots above, there are two noteable features in the dataset:

@@

\subsection{Build Classifier}
The dataset is now split into training, testing and validation sets. 60\% of the data is used for training with 20\% used for testing and validation respectivley:
\begin{Schunk}
\begin{Sinput}
> set.seed(57)
> # Split into train test and validation sets
> index <- sample(c(1:3), size = nrow(df), replace = TRUE, prob = c(.6, .2, .2))
> df_train <- df[index == 1,]
> df_test <- df[index == 2,]
> df_valid <- df[index == 3,]
\end{Sinput}
\end{Schunk}

@@

Here, a parameter grid is defined and stored as a dataframe to be accessed as each candidate model is trained
\begin{Schunk}
\begin{Sinput}
> num_attributes <- ncol(df_train)
> #build a parameter grid
> # Random forest
> mtry <- as.integer(c(num_attributes * 0.25, num_attributes / 3, num_attributes * 0.5, num_attributes * 0.8))
> nodesize <- c( 3, 5, 20)
> ntree <- c(200)
> PG<- as.data.frame(expand.grid(mtry=mtry, nodesize=nodesize,
+                                          ntree=ntree, stringsAsFactors=F))
\end{Sinput}
\end{Schunk}
Now, we train up a random forest on the training set for each combination of parameters in the parameter grid. \\
For each combination of parameters, the resulting model is tested on the evaluation set and the accuracy calculated.
The resulting accuracy from each parameter combination is saved in the 'Accuracy' column of the parameter grid table \textit{full output not shown here for brevity}:
\begin{Schunk}
\begin{Sinput}
>set.seed(57)
> for (i in c(1:nrow(PG))){
+   mtry <- PG[i, "mtry"]
+   nodesize <- PG[i, "nodesize"]
+   ntree <- PG[i, "ntree"]
+ 
+   temp_model <- randomForest(formula(df_train) , data=df_train, mtry=mtry, ntree=ntree, nodesize=nodesize)
+   predictions <- predict(temp_model , df_valid)
+   cm<- confusionMatrix(predictions,df_valid$won)
+   accuracy <- cm$overall['Accuracy']
+   PG[i,'Accuracy'] <- accuracy
+   print(i)
+ }
\end{Sinput}

\end{Schunk}

The parameters which produced the best model are selected and that model is evaluated on the testing set to give a final accuracy for the random forest classifier.
\begin{Schunk}
\begin{Sinput}
> #assess best model on test set
> PG <- PG%>%
+   arrange(desc(Accuracy))
> mtry <- PG[1, "mtry"]
> nodesize <- PG[1, "nodesize"]
> ntree <- PG[1, "ntree"]
>set.seed(57)
> best_model <- randomForest(formula(df_train) , data=df_train, mtry=mtry, ntree=ntree, nodesize=nodesize , importance=T)
> predictions <- predict(temp_model , df_valid)
> confusionMatrix(predictions,df_valid$won)
\end{Sinput}
\begin{Soutput}
Confusion Matrix and Statistics

@@

       'Positive' Class : -1              
\end{Soutput}
\end{Schunk}

@@

The ROC curve for the predictions is plotted below, with an \textbf{AUC of 0.579}. Again, this is far from a perfect classifier but does suggest some bias in the game which could potentially be exploited by a sufficiently well-trained AI:

@@

The variable importances are also of interest. In this case, each variable represents whether a particular character was used by the team, or the opposing team. So, plotting the importance of each character gives insights into any exploits that could be used to beat a team (ie by selecting or not selecting that hero). The realtive importances of the top 2 most important heroes are plotted below:

\begin{Schunk}
\begin{Sinput}
>#save variable importances
>varImps <- varImp(best_model)
>colnames(varImps) <- c('importance'," ")
>varImps <- varImps[order(-varImps$importance),] 
>varImps$names <- rownames(varImps)

@@

\end{Sinput}
\end{Schunk}

@@

It should also be noted that the 'enchantress' hero was not particularly popular or unpopular (\ref{home}), which further suggests this hero is of high importance.

@@

First the required libraries are loaded:
\begin{Schunk}
\begin{Sinput}
> library(data.table)
> library(RMOA)
> library(stream)
\end{Sinput}
\end{Schunk}

A validation set will not be used in this case since the aim is to demonstrate a streaming classifier; parameter tuning was demonstrated in the above section. So, the validation and testing set from the above section are combined to create a new testing set. The stream classifier will therefore be trained on 60\% of the original dataset:
\begin{Schunk}
\begin{Sinput}
> df_test <- bind_rows(df_test,df_valid)
> 
\end{Sinput}
\end{Schunk}
Several classifier types were tried but that which gave the quickest improvement in accuracy was the 'Ozaboost' classifier. This is a boosted model created specifically for streaming \cite{6934280}. A Hoeffding tree is used as the base learner.
\begin{Schunk}
\begin{Sinput}
> mymodel <- OzaBoost(baseLearner="trees.HoeffdingTree", ensemblesize=30)
\end{Sinput}
\end{Schunk}
A stream object is created to pass the data incrementally to the model. It was decided to stream data in chunks of 100 instances. For the training set of ~60000 rows, this will give ~600 chunks overall. The dataset has over 100 dimensions so 100 rows should contain enough data for the model to meaningfully update itself on every iteration.
\begin{Schunk}
\begin{Sinput}
> # Create a stream 
> dfStream <-datastream_dataframe(data=as.data.table(df_train))
> # other variables for training
> chunk <- 100
> #use the chunk size and size of the training set to define the number of turns required for training
> turns <- (nrow(dfStream$data)/chunk)-1
> turns <- floor(turns)
\end{Sinput}
\end{Schunk}
We make a similar stream object for the testing data. This will allow for testing concurrent to training ie, the model will be tested after every training iteration. This will allow for early stopping if a desired accuracy is reached before the full dataset has been used for training.\\
Note, the size of the testing chunks is defined by taking the size of the training chunks and scaling it down in proportion to the test/training set size. This ensures there are an equal number of training and testing chunks, so testing can be carried out after every training iteration.
\begin{Schunk}
\begin{Sinput}
> #make a test stream
> test_stream <- datastream_dataframe(data=as.data.table(df_test))
> # other variables for testing
> test_chunk <- floor(100 / (nrow(df_train)/nrow(df_test)))
\end{Sinput}
\end{Schunk}
Training is performed on a single chunk of data. This is achieved by retrieving a chunk from the stream object. The chunk is then used as training data for the model defined above:
\begin{Schunk}
\begin{Sinput}
> ## first sample (train) - retrieves first 100 records ##
> set.seed(57)
> sample <- dfStream$get_points(dfStream, n = chunk,
+                               outofpoints = c("stop", "warn", "ignore"))
> ## Train the first chunk
> 
> myboostedclassifier <- trainMOA(model = mymodel,
+                                 formula = won ~.,
+                                 data = datastream_dataframe(sample))
\end{Sinput}
\end{Schunk}
A single chunk of test data is also taken to be used for testing on this initial training iteration:
\begin{Schunk}
\begin{Sinput}
> test_sample <- test_stream$get_points(test_stream, n = test_chunk,
+                                       outofpoints = c("stop", "warn", "ignore"))
\end{Sinput}
\end{Schunk}
The test sample is used to evaluate the accuracy of the initial training run. It is as good as random guessing, so unsurprisingly more data will be required to build a useful classifier:
\begin{Schunk}
\begin{Sinput}
> ## Do some prediction to test the model
> predictions <- predict(myboostedclassifier, test_sample)
> table(sprintf("Actuals: %s", test_sample$won),
+       sprintf("Predicted: %s", predictions))
\end{Sinput}
\begin{Soutput}
              Predicted: -1 Predicted: 1
  Actuals: -1            17           13
  Actuals: 1             20           15
\end{Soutput}
\begin{Sinput}
> # calculate accuracy
> cat("Accuracy is: ", sum(predictions==test_sample$won)/nrow(test_sample)*100,"%")
\end{Sinput}
\begin{Soutput}
Accuracy is:  49.23077 %
\end{Soutput}
\end{Schunk}
The results for each training/testing iteration will be held in a vector for later analysis:
\begin{Schunk}
\begin{Sinput}
> # hold results in a vector
> accuracies <- c()
> #reset the test stream 
> test_stream$reset()
\end{Sinput}
\end{Schunk}
Now the model is incrementally trained and tested by feeding in chunks sequentially. For each iteration a training chunk is presented and the model is incrementally trained on that chunk. Then a testing chunk is presented to assess the performance of the model for each iteration, printing the current accuracy to the console. \textit{Full output not included in this document for brevity}.

\begin{Schunk}
\begin{Sinput}
>#train over the stream
>set.seed(57)
>for (i in 1:turns){
>  # next sample
> sample <- dfStream$get_points(dfStream, n = chunk,
+                               outofpoints = c("stop", "warn", "ignore"))
>  test_sample <- test_stream$get_points(test_stream, n = test_chunk,
+                                       outofpoints = c("stop", "warn", "ignore"))
>  ## Update the trained model with the new chunks
>  myboostedclassifier <- trainMOA(model = myboostedclassifier$model,
+                                  formula = won ~ .,
+                                  data = datastream_dataframe(sample),
+                                  reset = FALSE,trace = FALSE)
>  cat("chunk: ",i,"\n")

@@

\end{Sinput}
\end{Schunk}

The final accuracy achieved was 58.1\%, which is actually higher than for the best non-streaming model. This may be due to the use of a different model type which performed better on the given dataset. This is also a reasonably high accuracy for this problem - as stated earlier, anything above 50\% is considered a positive result since an ideal game should be perfectly balanced.

The improvement in accuracy with training/testing iteration is plotted in figure \ref{fig2}. We see that the classifier was rather erratic in accuracy as more data was presented to it. The general trend was for accuracy to steadily increase, although peak accuracy was reached aroumd chunk 350, suggesting only about half the data was required to fit a model. However, accuracy was increasing towards the end of the streaming process, so a larger dataset may have given even better results.

@@

@@

First, the dataset is loaded into the workspace, along with all the required libraries:

\begin{Schunk}
\begin{Sinput}
> library(dplyr)
> library(tm)
> library(SnowballC)
> library(RColorBrewer)
> library(wordcloud)
> library(ggplot2)
> library(gridExtra)
> library(graph)
> library(Rgraphviz)
> library(RTextTools)
> df <- read.csv("leaveRemainTweets_CW.csv")
\end{Sinput}
\end{Schunk}
The 'leave' and 'remain' tweets are seperated and stored in different objects. We also check that we have captured all tweets by seperating by label (ie there a no unlabelled tweets, or any with labels outwith 'leave' or 'remain'):
\begin{Schunk}
\begin{Sinput}
> #seperate dataframes for leave and remain tweets
> leave_tweets <- df%>%
+   filter(label=="Leave")
> remain_tweets <- df%>%
+   filter(label=="Remain")
> #check we have captured all the tweets
> nrow(df)==(nrow(leave_tweets) + nrow(remain_tweets))
\end{Sinput}
\begin{Soutput}
[1] TRUE
\end{Soutput}
\end{Schunk}
It is important to ensure the dataset is balanced, ie there are a similar number of leave and remain tweets. There are more leave tweets than remain ones, but the difference isn't too great:
\begin{Schunk}
\begin{Sinput}
> nrow(leave_tweets)
\end{Sinput}
\begin{Soutput}
[1] 1254
\end{Soutput}
\begin{Sinput}
> nrow(remain_tweets)
\end{Sinput}
\begin{Soutput}
[1] 1029
\end{Soutput}
\end{Schunk}

In order to analyse the text, a corpus will be built. This will be achieved through a dedicated function defined below. This function performs the following pre-processing steps:

\begin{itemize}
  \item convert the encoding to UTF-8
  \item convert all text to lowercase - the case doesn't give us any extra information.
  \item remove punctuation, numbers and URLs
  \item remove the following common words, none of which convey any real informatiom: "RT","rt","EU","eu","brexit","euref"
  \item remove words CONTAINING the following terms (these are often used in conjunction with a hashtag): 'vote', 'leave', 'remain', 'stronger'.'referendum'.
  \item remove all standard English stopwords
  \item strip out any whitespace.
\end{itemize}

>>>>

To study the dataset in more detail, let's load it into the workspace, along with the required libraries. The original dataset, as downloaded, is already split into a training and testing set. However, in order to ensure the split as indeed random and stratified, the data was re-combined into a single dataset.
\hspace{1cm}

@@

\hspace{1cm}

@@

\begin{itemize}
  \item The typing is incorrect as imported - the types should all be factors
  \item The dataset is quite sparse
  \item The columns are not named. They are defined in the readme for the dataset so we will add names later
\end{itemize}
\hspace{1cm}

\begin{Schunk}
\begin{Sinput}
> library(xtable)
> print(xtable(head(df)))
> str(df)
> names(df)
\end{Sinput}
\end{Schunk}
Let's also check the size of the dataset:
\begin{Schunk}
\begin{Sinput}
> #record number of rows and columns
> paste('number of columns =' , ncol(df) , '. number of rows =', nrow(df))
\end{Sinput}
\begin{Soutput}
[1] "number of columns = 117 . number of rows = 102942"
\end{Soutput}
\end{Schunk}
\hspace{1cm} 
Now let's check the class distribution (ie do we have an approximately equal number of team 1 wins as team 2 wins?).
The distribution is indeed close to equal so we do not need to worry about class imbalance later on. It is interesting to note there is some imbalance, the reason for this is not clear but probably has something to do with the manner in which the data was collected.

\hspace{1cm} 
\begin{Schunk}
\begin{Sinput}
> #check value distribution of response variable column
> table(df[,1])
\end{Sinput}
\end{Schunk}
\hspace{1cm}

@@

An advantage of this dataset is there are no missing values. This is not surprising as the data was captured using the Dota 2 API. Here we also check that each team has an equal number of heroes which is a requirement for a game:
\hspace{1cm}

\begin{Schunk}
\begin{Sinput}
> #check for missing values (there are none)
> sum(complete.cases(df))==nrow(df)
\end{Sinput}
\begin{Soutput}
[1] TRUE
\end{Soutput}
\begin{Sinput}
> #check there are equal number of heroes present in each team (hero values for all rows
># should sum to zero)
> sum((rowSums(df[5:ncol(df)]))) == 0
\end{Sinput}
\begin{Soutput}
[1] TRUE
\end{Soutput}
\end{Schunk}
\hspace{1cm}

As discussed above, some preprocessing is required. First, we convert all numeric columns to factors:

\hspace{1cm} 
\begin{Schunk}
\begin{Sinput}
> df[sapply(df, is.numeric)] <- lapply(df[sapply(df, is.numeric)], as.factor)
\end{Sinput}
\end{Schunk}
\hspace{1cm}

The column names are added in two stages. The first four columns are named manually as specified in the dataset description.\\
The remaining columns represent the individual heros. The column names are extracted from the .json file supplied with the dataset:

\hspace{1cm} 
\begin{Schunk}
\begin{Sinput}
> #add column names to the first few columns
> names(df)[1:4] <- c('won','cluster_id','game_mode','game_type')
> #populate the other column names
> #load in json file and use it to populate column names
> hero_names <- fromJSON(file ="dota_dataset\\heroes.json")
> for ( i in c(1:length(hero_names$heroes))){
+   names(df)[i+4] <- hero_names$heroes[[i]]$name
+ }
\end{Sinput}
\end{Schunk}
\hspace{1cm}

Here we drop columns that are not related to heros (this analysis is concerned only with hero choice so we drop game type and location related columns). 
One column has the same value for every entry. This was noticed during the analysis stage. The column represents a mandatory hero which muct be included in the team. Since it conveys no information it is dropped:

\hspace{1cm} 
\begin{Schunk}
\begin{Sinput}
> #drop unwanted columns
> df <- df%>%
+   select(-c(lina, cluster_id , game_mode , game_type))
\end{Sinput}
\end{Schunk}
\hspace{1cm}

@@

\hspace{1cm} 
\begin{Schunk}
\begin{Sinput}
>#check variable balancing
>numeric_df <- sapply(df,function(x){as.numeric(as.character(x))})%>%
+  as.data.frame()%>%
+  select(-seq(1,4))

@@

>ggplot(away_team_heros,aes(x=name,y=.))+
+  geom_bar(stat="identity")+
+ theme(axis.text.x = element_text(angle = 90, hjust = 1,size=7))+
+  labs(title="number of times each hero was chosen by the away team")+
+  xlab("hero name")+
+  ylab("number of games the hero was picked")
\end{Sinput}
\end{Schunk}
\hspace{1cm}

@@

Inspecting Figures \ref{home} and \ref{away}, there are two noteable features in the dataset:

@@

\subsection{Build Classifier}
The dataset is now split into training, testing and validation sets. 60\% of the data is used for training with 20\% used for testing and validation respectivley:

\hspace{1cm} 
\begin{Schunk}
\begin{Sinput}
> set.seed(57)
> # Split into train test and validation sets
> index <- sample(c(1:3), size = nrow(df), replace = TRUE, prob = c(.6, .2, .2))
> df_train <- df[index == 1,]
> df_test <- df[index == 2,]
> df_valid <- df[index == 3,]
\end{Sinput}
\end{Schunk}
\hspace{1cm}

@@

Here, a parameter grid is defined and stored as a dataframe to be accessed as each candidate model is trained
\hspace{1cm} 
\begin{Schunk}
\begin{Sinput}
> num_attributes <- ncol(df_train)
> #build a parameter grid
> # Random forest
> mtry <- as.integer(c(num_attributes * 0.25,
+	 num_attributes / 3, num_attributes * 0.5, num_attributes * 0.8))
> nodesize <- c( 3, 5, 20)
> ntree <- c(200)
> PG<- as.data.frame(expand.grid(mtry=mtry, nodesize=nodesize,
+                                          ntree=ntree, stringsAsFactors=F))
\end{Sinput}
\end{Schunk}
\hspace{1cm} 
Now, we train up a random forest on the training set for each combination of parameters in the parameter grid. \\
For each combination of parameters, the resulting model is tested on the evaluation set and the accuracy calculated.
The resulting accuracy from each parameter combination is saved in the 'Accuracy' column of the parameter grid table \textit{full output not shown here for brevity}:
\hspace{1cm} 
\begin{Schunk}
\begin{Sinput}
>set.seed(57)
> for (i in c(1:nrow(PG))){
+   mtry <- PG[i, "mtry"]
+   nodesize <- PG[i, "nodesize"]
+   ntree <- PG[i, "ntree"]
+ 
+   temp_model <- randomForest(formula(df_train) , data=df_train, mtry=mtry, ntree=ntree,
+	 nodesize=nodesize)
+   predictions <- predict(temp_model , df_valid)
+   cm<- confusionMatrix(predictions,df_valid$won)
+   accuracy <- cm$overall['Accuracy']
+   PG[i,'Accuracy'] <- accuracy
+   print(i)
+ }
\end{Sinput}

\end{Schunk}
\hspace{1cm}

The parameters which produced the best model are selected and that model is evaluated on the testing set to give a final accuracy for the random forest classifier.
\hspace{1cm} 
\begin{Schunk}
\begin{Sinput}
> #assess best model on test set
> PG <- PG%>%
+   arrange(desc(Accuracy))
> mtry <- PG[1, "mtry"]
> nodesize <- PG[1, "nodesize"]
> ntree <- PG[1, "ntree"]
>set.seed(57)
> best_model <- randomForest(formula(df_train) , data=df_train, mtry=mtry, ntree=ntree, nodesize=nodesize , importance=T)
> predictions <- predict(temp_model , df_valid)
> confusionMatrix(predictions,df_valid$won)
\end{Sinput}
\begin{Soutput}

Confusion Matrix and Statistics

@@

       'Positive' Class : -1              
\end{Soutput}
\end{Schunk}
\hspace{1cm}

@@

The ROC curve for the predictions is plotted in Figure \ref{fig02}, with an \textbf{AUC of 0.579}. Again, this is far from a perfect classifier but does suggest some bias in the game which could potentially be exploited by a sufficiently well-trained AI:

@@

The variable importances are also of interest. In this case, each variable represents whether a particular character was used by the team, or the opposing team. So, plotting the importance of each character gives insights into any exploits that could be used to beat a team (ie by selecting or not selecting that hero). The realtive importances of the top 2 most important heroes are plotted below:
\hspace{1cm} 
\begin{Schunk}
\begin{Sinput}
>#save variable importances
>varImps <- varImp(best_model)
>colnames(varImps) <- c('importance'," ")
>varImps <- varImps[order(-varImps$importance),] 
>varImps$names <- rownames(varImps)

@@

\end{Sinput}
\end{Schunk}
\hspace{1cm}

@@

It should also be noted that the 'enchantress' hero was not particularly popular or unpopular (Figure \ref{home}), which further suggests this hero is of high importance.

@@

First the required libraries are loaded:
\hspace{1cm} 
\begin{Schunk}
\begin{Sinput}
> library(data.table)
> library(RMOA)
> library(stream)
\end{Sinput}
\end{Schunk}
\hspace{1cm}

A validation set will not be used in this case since the aim is to demonstrate a streaming classifier; parameter tuning was demonstrated in the above section. So, the validation and testing set from the above section are combined to create a new testing set. The stream classifier will therefore be trained on 60\% of the original dataset:
\hspace{1cm} 
\begin{Schunk}
\begin{Sinput}
> df_test <- bind_rows(df_test,df_valid)
> 
\end{Sinput}
\end{Schunk}
\hspace{1cm} 
Several classifier types were tried but that which gave the quickest improvement in accuracy was the 'Ozaboost' classifier. This is a boosted model created specifically for streaming \cite{6934280}. A Hoeffding tree is used as the base learner.
\hspace{1cm} 
\begin{Schunk}
\begin{Sinput}
> mymodel <- OzaBoost(baseLearner="trees.HoeffdingTree", ensemblesize=30)
\end{Sinput}
\end{Schunk}
\hspace{1cm} 
A stream object is created to pass the data incrementally to the model. It was decided to stream data in chunks of 100 instances. For the training set of ~60000 rows, this will give ~600 chunks overall. The dataset has over 100 dimensions so 100 rows should contain enough data for the model to meaningfully update itself on every iteration.
\hspace{1cm} 
\begin{Schunk}
\begin{Sinput}
> # Create a stream 
> dfStream <-datastream_dataframe(data=as.data.table(df_train))
> # other variables for training
> chunk <- 100
> #use the chunk size and size of the training set to define the number of turns required for training
> turns <- (nrow(dfStream$data)/chunk)-1
> turns <- floor(turns)
\end{Sinput}
\end{Schunk}
\hspace{1cm} 
We make a similar stream object for the testing data. This will allow for testing concurrent to training ie, the model will be tested after every training iteration. This will allow for early stopping if a desired accuracy is reached before the full dataset has been used for training.\\
Note, the size of the testing chunks is defined by taking the size of the training chunks and scaling it down in proportion to the test/training set size. This ensures there are an equal number of training and testing chunks, so testing can be carried out after every training iteration.
\hspace{1cm} 
\begin{Schunk}
\begin{Sinput}
> #make a test stream
> test_stream <- datastream_dataframe(data=as.data.table(df_test))
> # other variables for testing
> test_chunk <- floor(100 / (nrow(df_train)/nrow(df_test)))
\end{Sinput}
\end{Schunk}
\hspace{1cm} 
Training is performed on a single chunk of data. This is achieved by retrieving a chunk from the stream object. The chunk is then used as training data for the model defined above:
\hspace{1cm} 
\begin{Schunk}
\begin{Sinput}
> ## first sample (train) - retrieves first 100 records ##
> set.seed(57)
> sample <- dfStream$get_points(dfStream, n = chunk,
+                               outofpoints = c("stop", "warn", "ignore"))
> ## Train the first chunk
> 
> myboostedclassifier <- trainMOA(model = mymodel,
+                                 formula = won ~.,
+                                 data = datastream_dataframe(sample))
\end{Sinput}
\end{Schunk}
\hspace{1cm} 
A single chunk of test data is also taken to be used for testing on this initial training iteration:
\hspace{1cm} 
\begin{Schunk}
\begin{Sinput}
> test_sample <- test_stream$get_points(test_stream, n = test_chunk,
+                                       outofpoints = c("stop", "warn", "ignore"))
\end{Sinput}
\end{Schunk}
\hspace{1cm} 
The test sample is used to evaluate the accuracy of the initial training run. It is as good as random guessing, so unsurprisingly more data will be required to build a useful classifier:
\hspace{1cm} 
\begin{Schunk}
\begin{Sinput}
> ## Do some prediction to test the model
> predictions <- predict(myboostedclassifier, test_sample)
> table(sprintf("Actuals: %s", test_sample$won),
+       sprintf("Predicted: %s", predictions))
\end{Sinput}
\begin{Soutput}

              Predicted: -1 Predicted: 1
  Actuals: -1            17           13
  Actuals: 1             20           15
\end{Soutput}
\begin{Sinput}
> # calculate accuracy
> cat("Accuracy is: ", sum(predictions==test_sample$won)/nrow(test_sample)*100,"%")
\end{Sinput}
\begin{Soutput}
Accuracy is:  49.23077 %
\end{Soutput}
\end{Schunk}
\hspace{1cm} 
The results for each training/testing iteration will be held in a vector for later analysis:
\hspace{1cm} 
\begin{Schunk}
\begin{Sinput}
> # hold results in a vector
> accuracies <- c()
> #reset the test stream 
> test_stream$reset()
\end{Sinput}
\end{Schunk}
\hspace{1cm} 
Now the model is incrementally trained and tested by feeding in chunks sequentially. For each iteration a training chunk is presented and the model is incrementally trained on that chunk. Then a testing chunk is presented to assess the performance of the model for each iteration, printing the current accuracy to the console. \textit{Full output not included in this document for brevity}.
\hspace{1cm} 
\begin{Schunk}
\begin{Sinput}
>#train over the stream
>set.seed(57)
>for (i in 1:turns){
>  # next sample
> sample <- dfStream$get_points(dfStream, n = chunk,
+                               outofpoints = c("stop", "warn", "ignore"))
>  test_sample <- test_stream$get_points(test_stream, n = test_chunk,
+                                       outofpoints = c("stop", "warn", "ignore"))
>  ## Update the trained model with the new chunks
>  myboostedclassifier <- trainMOA(model = myboostedclassifier$model,
+                                  formula = won ~ .,
+                                  data = datastream_dataframe(sample),
+                                  reset = FALSE,trace = FALSE)
>  cat("chunk: ",i,"\n")

@@

\end{Sinput}
\end{Schunk}
\hspace{1cm}

\hspace{1cm}

@@

\subsection{Results}
The final accuracy achieved was 58.1\%, which is actually higher than for the best non-streaming model. This may be due to the use of a different model type which performed better on the given dataset. This is also a reasonably high accuracy for this problem - as stated earlier, anything above 50\% is considered a positive result since an ideal game should be perfectly balanced.

The improvement in accuracy with training/testing iteration is plotted in figure \ref{fig2}. We see that the classifier was rather erratic in accuracy as more data was presented to it. This is unsurprising as the dataset is inherantly noisy, with many unseen variables contributing to a team's chance of winning a game. The general trend, however, was for accuracy to steadily increase, although peak accuracy was reached around chunk 350, suggesting only about half the data was required to fit a model. However, accuracy was increasing towards the end of the streaming process, so a larger dataset may have given even better results. Future work could stream a dataset of a significantly larger size to increase accuracy.\\

\subsection{Future Work}
A more involved study in the future could include other variables to predict whether a team will win or not. The original dataset used in this study included location data, along with game type. These variables were excluded in this case to simplify the analysis. Dota2 is well-known for the wide-range of possible variables within a given game. Future studies could consider variables such as map type, player skill and experience. Furthermore, a useable AI would require a dynamic algorithm which could adapt tactics during a game as the situation changes. The results here may be used for hero selection, but to beat a human player, many more factors would require consideration. \\

Another interesting area for future exploration would be the relative importance of various heros. This study found one particular hero to be dominant. However, it would be useful to know when to actually pick this hero (ie if the away team picks hero 'x', the home team should pick hero 'y' for gain an advantage of 'z'\%). A simple market basket type analysis may be sufficient to give insights into the interactions between heros, while more complex Markov models \cite{6080982} or limited Monte Carlo simulations may give better insights.

@@

First, the dataset is loaded into the workspace, along with all the required libraries:
\hspace{1cm} 
\begin{Schunk}
\begin{Sinput}
> library(dplyr)
> library(tm)
> library(SnowballC)
> library(RColorBrewer)
> library(wordcloud)
> library(ggplot2)
> library(gridExtra)
> library(graph)
> library(Rgraphviz)
> library(RTextTools)
> df <- read.csv("leaveRemainTweets_CW.csv")
\end{Sinput}
\end{Schunk}
\hspace{1cm} 
The 'leave' and 'remain' tweets are seperated and stored in different objects. We also check that we have captured all tweets by seperating by label (ie there a no unlabelled tweets, or any with labels outwith 'leave' or 'remain'):
\hspace{1cm} 
\begin{Schunk}
\begin{Sinput}
> #seperate dataframes for leave and remain tweets
> leave_tweets <- df%>%
+   filter(label=="Leave")
> remain_tweets <- df%>%
+   filter(label=="Remain")
> #check we have captured all the tweets
> nrow(df)==(nrow(leave_tweets) + nrow(remain_tweets))
\end{Sinput}
\begin{Soutput}
[1] TRUE
\end{Soutput}
\end{Schunk}
\hspace{1cm} 
It is important to ensure the dataset is balanced, ie there are a similar number of leave and remain tweets. There are more leave tweets than remain ones, but the difference isn't too great:
\hspace{1cm} 
\begin{Schunk}
\begin{Sinput}
> nrow(leave_tweets)
\end{Sinput}
\begin{Soutput}
[1] 1254
\end{Soutput}
\begin{Sinput}
> nrow(remain_tweets)
\end{Sinput}
\begin{Soutput}
[1] 1029
\end{Soutput}
\end{Schunk}
\hspace{1cm} 
In order to analyse the text, a corpus will be built. This will be achieved through a dedicated function defined below. This function performs the following pre-processing steps:
